% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

% Enable hyperlinks
\setupinteraction[state=start, color=middleblue]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=20mm, cutspace=0mm,
                 topspace=20mm, bottomspace=20mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[Cambria]


\setupwhitespace[medium]

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=709cb7]
\definecolor[rulecolor][h=709cb7]

\setupblackrules[width=25mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext

\section[aytuğ-murat-aydin]{Aytuğ Murat AYDIN}

\thinrule

\startblockquote
Generalist Software Engineer, experienced in full stacked development,
in search of new challenge.
\stopblockquote

\thinrule

\subsection[education]{Education}

\startdescription{2010-2012 (No Graduation)}
  {\bf MSC, Computer Science}; Bilkent University (Ankara/Turkey)

  {\em Thesis title: Software Architectural Analysis of Simulation
  Systems}
\stopdescription

\startdescription{2005-2010}
  {\bf BSc, Computer Science}; Bilkent University (Ankara/Turkey)

  {\em CGPA: 3.12}
\stopdescription

\subsection[experience]{Experience}

{\bf Onur Inc. (July 2014-):}

\startitemize
\item
  Developed Rest Webservice Framework with Python and Flask
\item
  Full Stacked Development with Backbone.js, Django and Node.js
\stopitemize

{\bf KorvusSoft (April 2013- July 2014):}

\startitemize
\item
  Involved in design and development of Zettabahn project. Zettabahn
  offers big data platform that accepts incoming stream of tupples to
  make analytic operations and stores them in distributed fashion. It
  uses Hadoop for DFS, HBase as NoSQL solution, Twitter Storm for
  distributed stream processing.
\item
  Worked on design and development of Social AD which is a Social Media
  Advertising Application which targets thousands of users. Developed
  both UI and backend of the system, as well as database design. I
  designed software models, database design and architecture of the
  system.
\item
  Worked as a part of the team for development of Cloud Social Media
  Monitoring application. This application has a multi-tenant
  architecture and has sub-units like Scoring Social Media Users. I
  developed Webservices for serving both as provinding data to UI and as
  storing data into Hbase for backend of the application. I developed
  distributed Stream processing infrastructure of the system using open
  source Storm library. Besides I also developed User Interface using
  Ruby on Rails.
\item
  Developed Question and Answer platform using Ruby on Rails and
  Postgresql. This application is developed in a very short period of
  time and maintained according to the needs of the client.
\item
  Developed a Mass E-Mailing service using Ruby on Rails, Icewarp Mail
  Server and Mysql. This application can handle the operation of sending
  100.000 emails daily.
\stopitemize

{\bf Meteksan Defense Inc. (June 2010- April 2013):}

As a software engineer, I was a part of team that developed one of the
most important Naval Simulation System projects in Turkey.:

\startitemize
\item
  Designed and Developed System Model and Inventory Generator using C++,
  QT and Oracle DB
\item
  Designed and Developed Scenario Generation Tool using C++, QT and
  Oracle DB
\item
  Involved in development of Analysis and Report Tool using C\#, C++,
  QT, DevExpress, Oracle DB and Sqlite
\item
  Designed and Developed Employee Evaluation Application using PHP and
  Mysql
\item
  Designed and Developed Employee Satisfaction Survey with abilities of
  reporting using Python, Django and Sqlite
\item
  Designed and Developed ERP application for Business Development
  Division using PHP and Mysql
\stopitemize

\subsection[technical-experience]{Technical Experience}

\startdescription{Technical Tools}
  {\bf Programming Languages:} Java, C/C++, C\#, Ruby, Python, PHP,
  JavaScript

  {\bf Libraries:} JUnit, Boost, QT, Ruby on Rails, Django, Primefaces,
  Storm, Devexpress, OpenCV, Jquery, Backbone.js, Node.js

  {\bf Database:} Oracle 11g R2, Mysql, Postgresql, Sqlite, Nosql(Hbase)

  {\bf Operating Systems:} Linux(Redhat, Centos, Fedora, Ubuntu),
  Windows(98-Windows 8)

  {\bf Web Servers:} Apache, Nginx, Tomcat, Thin, Unicorn

  {\bf Source Control:} Git, Mercurial, SVN

  {\bf Technical Tools:} Eclipse, Netbeans, VIM, Sublime Text,
  Enterprise Architect

  {\bf Software Methodlogies:} Object Oriented, Aspect Oriented and
  Model Driven Software Development, Big Data and Distributed Computing

  {\bf Miscellaneous:} Memcached, Redis, Flask, RabbitMq
\stopdescription

\subsection[side-projects]{Side Projects}

\startdescription{turkishsixpacks}
  turkishsixpacks.com, an online magazine for Fitness and Aesthetics
  enthusiasts. I personally wrote and translated over 100 articles and
  interviewed more than 20 athletes.

  \startitemize[packed]
  \item
    Works on Wordpress CMS
  \stopitemize
\stopdescription

\startdescription{bireyselantrenor}
  Online Listing Application for Personal Trainers Developed with
  {\bf Ruby on Rails}, {\bf Jquery}, {\bf Mysql} and {\bf HTML5}
\stopdescription

\startdescription{Image Recognition Tool}
  Application for detecting static objects from moving Camera and moving
  objects from static camera. Developed with {\bf C++}, {\bf OpenCV} and
  {\bf Matlab}
\stopdescription

\subsection[awards-and-certifications]{Awards and Certifications}

\startdescription{2010-2012}
  Tuition scholarship during graduate study by Bilkent University
\stopdescription

\startdescription{2005-2010}
  Full scholarship during undergraduate study by Bilkent University
\stopdescription

\startdescription{2005}
  Among top 500 students in University Entrance Exam
\stopdescription

\subsection[additional-skills-and-information]{Additional Skills and
Information}

\startitemize
\item
  Birthdate : 12/23/1987
\item
  E-Mail Address:
  \useURL[url1][mailto:aytugmurataydin@gmail.com][][\hyphenatedurl{aytugmurataydin@gmail.com}]\from[url1]
\item
  Website Address:
  \useURL[url2][http://aytugmurataydin.com][][\hyphenatedurl{http://aytugmurataydin.com}]\from[url2]
\item
  Spoken Languages:

  \startitemize[packed]
  \item
    Turkish (native speaker)
  \item
    English (Fluent)
  \item
    German (Basic)
  \stopitemize
\item
  Weight Lifting. Fitness
\item
  Blogging, writing, reading about Technology
\stopitemize

\thinrule

\startblockquote
• +90 (533) 716 5329 • Ankara, TURKEY
\stopblockquote

\stoptext
